Peaks and valleys of prolatin-related gene expression during pigeon parental care stages

### 2019-09-06 docs/characterization_manuscript.Rmd
now with abstract

---
title: Peaks and valleys of prolatin-related gene expression during pigeon parental care stages
author:
  - name: Rayna M Harris
    email: rmharris@ucdavis
    affiliation: UC Davis
    corresponding: "rmharris@ucdavis"
  - name: Suzanne Austin
    affiliation: UC Davis
  - name: Andrew Lang
    affiliation: UNH
  - name: Matthew MacManes
    affiliation: UNH
  - name: Rebecca M Calisi
    affiliation: UC Davis           
address:
  - code: UC Davis
    address: UC Davis, Davis, CA
  - code: UNH
    address: UNH, smalltown, NH
abstract: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
author_summary: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

>>>>

---
title: Peaks and valleys of prolatin-related gene expression during pigeon parental care stages
author:
  - name: Rayna M Harris
    email: rmharris@ucdavis
    affiliation: UC Davis
    corresponding: "rmharris@ucdavis"
  - name: Suzanne Austin
    affiliation: UC Davis
  - name: Andrew Lang
    affiliation: UNH
  - name: Matthew MacManes
    affiliation: UNH
  - name: Rebecca M Calisi
    affiliation: UC Davis           
address:
  - code: UC Davis
    address: UC Davis, Davis, CA
  - code: UNH
    address: UNH, smalltown, NH
abstract: |
  The goal of this research was to provide the most comprehensive gene expression profile of gene expression activity in the HPG axis of male and female rock doves to provide a deeper undertand of how the reproductive axis response to typical behavioral transitions associated with parental care. Here we used RNA sequencing to measure gene activity at 8 stages of the parental care cyle from nest building, to egg incubation, and through nestling care. Non-parental groups were added as controls, but gene expressions differences were assesed between and across all time points. The three tissue have unique signatures, but within each tissue we find minial sex differences. The pitutary samples displacy the msot plasticity in gene expression, with many changes in gene expression mirroring the typical rise and fall of circulating prolatin that peaks when chicks hatch. Our analysis provides new insight into how suites of genes respond in concert to the demands of offspring care.
author_summary: |
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
bibliography: mybibfile.bib
output: rticles::plos_article
csl: plos.csl
---

### 2019-09-06 docs/characterization_manuscript.tex
now with abstract

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Peaks and valleys of prolatin-related gene expression during pigeon
parental care stages} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rayna M Harris\textsuperscript{\getAff{UC Davis}}\textsuperscript{*},
Suzanne Austin\textsuperscript{\getAff{UC Davis}},
Andrew Lang\textsuperscript{\getAff{UNH}},
Matthew MacManes\textsuperscript{\getAff{UNH}},
Rebecca M Calisi\textsuperscript{\getAff{UC Davis}}\\
\bigskip
\textbf{\getAff{UC Davis}}UC Davis, Davis, CA\\
\textbf{\getAff{UNH}}UNH, smalltown, NH\\
\bigskip
* Corresponding author: rmharris@ucdavis\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Peaks and valleys of prolatin-related gene expression during pigeon
parental care stages} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Rayna M Harris\textsuperscript{\getAff{UC Davis}}\textsuperscript{*},
Suzanne Austin\textsuperscript{\getAff{UC Davis}},
Andrew Lang\textsuperscript{\getAff{UNH}},
Matthew MacManes\textsuperscript{\getAff{UNH}},
Rebecca M Calisi\textsuperscript{\getAff{UC Davis}}\\
\bigskip
\textbf{\getAff{UC Davis}}UC Davis, Davis, CA\\
\textbf{\getAff{UNH}}UNH, smalltown, NH\\
\bigskip
* Corresponding author: rmharris@ucdavis\\
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
The goal of this research was to provide the most comprehensive gene
expression profile of gene expression activity in the HPG axis of male
and female rock doves to provide a deeper undertand of how the
reproductive axis response to typical behavioral transitions associated
with parental care. Here we used RNA sequencing to measure gene activity
at 8 stages of the parental care cyle from nest building, to egg
incubation, and through nestling care. Non-parental groups were added as
controls, but gene expressions differences were assesed between and
across all time points. The three tissue have unique signatures, but
within each tissue we find minial sex differences. The pitutary samples
displacy the msot plasticity in gene expression, with many changes in
gene expression mirroring the typical rise and fall of circulating
prolatin that peaks when chicks hatch. Our analysis provides new insight
into how suites of genes respond in concert to the demands of offspring
care.
